\rule{\textwidth}{4pt}\\ \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payout Approximation in Discrete Space}\\[0.2cm] \rule{\textwidth}{2pt}

### 2025-02-12 latex/article.tex
80 symbols

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of L1 and L2 regularization}
\label{fig:regularization}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of L1 and L2 regularization methods for approximating a complex 
payout profile as a function of the underlying asset price at maturity. The target 
payout (solid black) combines linear, sinusoidal, and power-law segments. Both L2 
(dashed) and L1 (dash-dotted) regularization methods achieve good approximation 
using 9 strike prices, with L1 producing a sparser portfolio.}
\label{fig:regularization}
\end{figure}
